---
title: "rmetrics"
author: "Jonas Schropp"
date: "`r Sys.Date()`"
output: md_document
---

# Introduction

`rmetrics` is a R package to calculate a large variety of metrics to evaluate machine learning models and statistical models. It is primarily designed as a backend to my package `revaluate`, but will receive some work to make it worthwhile as a standalone package in the future.  

Metrics in the package can generally be classified into metrics for a *binary*, *multiclass* or *ordered* dependent variable, with the special case of binary dependent variables that are evaluated using upper and lower cutoffs and a grey area in between.

# Installation

You can install the package via github:

```{r, eval = FALSE}
devtools::install_github("https://github.com/jonas-schropp/rmetrics.git")
```

And load it with:
```{r echo = FALSE, include=FALSE}
devtools::load_all()
```

```{r eval = FALSE}
library(rmetrics)
```

# Usage

Let's calculate Aickin's alpha as an example:
```{r}
# Simulate some data
prediction <- rbinom(100, 1, 0.5)
reference <- rbinom(100, 1, prediction * 0.7)

tbl <- table(prediction, reference)

calc_aickin(tbl = tbl)
```

# Contribute to this project

If you want to contribute to this project, please get in touch!

If there is a metric you want to see in this package that is not available, please either submit a `feature request` or implement it yourself and submit a `pull request`.

# Planned features

This package is under active development. The current focus for development is 1) to implement more metrics for ordinal classifiers and 2) to make sure that all functions follow common design features. 


